Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-03 main_revision.tex
Updates from Overleaf

The impact of \emph{slatop} on fertilization was different at every site (figs. \ref{GPP_CN}, figures \ref{LAI_CN}). For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR).

\emph{froot\_leaf} had contrasting impacts at different sites.  At MET,  where low values increased the CO$_{2}$ fertilization, probably due to the increased drought stress under those conditions. At HVF, low \emph{froot\_leaf} decreased both CO$_{2}$ and N fertilization on account of higher initial LAI, mirroring the respnse to \emph{slatop}.

Low \emph{stem\_leaf} ratio caused lower responses to N fertilization CAX, NWR and HVF for GPP and LAI at  (Figures \ref{GPP_CN} and \ref{LAI_CN}), again mirroring the GPP-LAI non-linearity issue.  At NWR,  N limitation restricted CO$_{2}$ responses in general, but

 Correspondingly, adding Nitrogen in the low \emph{stem\_leaf} runs increases LAI substantially, but only has a very limited impact on GPP and NPP, given water limitations.

The $N_{costs}$ parameterization primarily impacts the respiration expended on N uptake and the availability of carbon for tissue growth thus, its impact is greatest for LAI (Figure \ref{LAI CO2 and N respones 2001}). At Caxiuan\~a, Niwot and Harvard forest, high  $N_{costs}$ resulted in stronger LAI responses to N fertilization, since these cases had higher N limitation in the first instance (Figure \ref{btran state}).  These high $N_{costs}$ scenarios also showed a slight increase in the CO$_{2}$ fertilization response, perhaps since their high N limitation was alleviated by extra assimilated carbon.   Low values of $N_{costs}$ were associated with low CO$_{2}$ responses (and vice versa) in particular at Caxiuana and Harvard Forest, which can be interpreted as a reflection of the lower C expenditure on N uptake in the control simulations.  While nitrogen uptake costs are important to the fertilization responses, they do not affect the total amount of N in the system, and therefore appeared to play a secondary role to the amount of N fixation available.

@@

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_y1999.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) for GPP, NPP, LAI and N$+{leaf}$ at the CAX, NWR, HVF and MET sites}
     \label{NR1 state}
 \end{figure}

>>>>

The impact of \emph{slatop} on fertilization was different at every site (figs. \ref{GPP_CN}, figures \ref{LAI_CN}). For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR). 
\emph{froot\_leaf} had contrasting impacts at different sites.  At MET,  where low values increased the CO$_{2}$ fertilization, probably due to the increased drought stress under those conditions. At HVF, low \emph{froot\_leaf} decreased both CO$_{2}$ and N fertilization on account of higher initial LAI, mirroring the respnse to \emph{slatop}.

Low \emph{stem\_leaf} ratio caused lower responses to N fertilization CAX, NWR and HVF for GPP and LAI at  (Figures \ref{GPP_CN} and \ref{LAI_CN}), again mirroring the NPP-LAI non-linearity issue.  At NWR,  N limitation restricted CO$_{2}$ responses, but at CAX and NWR the same type of response was seen.  At MET, lower \emph{stem\_leaf} allowed greater responses, plausibly from increasing the speed of the NPP/LAI feedback.

At all site, higher $N_{costs}$ increases the responsiveness of the system to N, and to a lesser extent CO$_{2}$.

parameterization primarily impacts the respiration expended on N uptake and the availability of carbon for tissue growth thus, its impact is greatest for LAI (Figure \ref{LAI CO2 and N respones 2001}). At Caxiuan\~a, Niwot and Harvard forest, high  $N_{costs}$ resulted in stronger LAI responses to N fertilization, since these cases had higher N limitation in the first instance (Figure \ref{btran state}).  These high $N_{costs}$ scenarios also showed a slight increase in the CO$_{2}$ fertilization response, perhaps since their high N limitation was alleviated by extra assimilated carbon.   Low values of $N_{costs}$ were associated with low CO$_{2}$ responses (and vice versa) in particular at Caxiuana and Harvard Forest, which can be interpreted as a reflection of the lower C expenditure on N uptake in the control simulations.  While nitrogen uptake costs are important to the fertilization responses, they do not affect the total amount of N in the system, and therefore appeared to play a secondary role to the amount of N fixation available.

@@

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_y1999.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) for GPP, NPP, LAI and N$+{leaf}$ at the CAX, NWR, HVF and MET sites}
     \label{state}
 \end{figure}
